Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-13 programlogic.tex
+

\todo[inline,color=red]{Colin says: Why are we talking about assertions for address translations here? It seems like we should
\todo[inelin]{Colin says: There's no explanation of the split 52+12 \emph{notation} here. If we added such an explanation
(maybe to where physical points-tos are introduced?) and moved this discussion to \ref{sec:overly-restrictive}, this is otherwise
a nice explanation}
discuss physical memory pointsto assertions in general first, then talk about this in \ref{sec:overly-restrictive}}
Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
\begin{itemize}
  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry entry amongst 512 (q1) respectively.
    \begin{lstlisting}[language=Coq]
      $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
    \end{lstlisting}
 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 (q2) respectively.
    \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
    \end{lstlisting}
  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry entry amongst 512 (q3) respectively.
\begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
    \end{lstlisting}
  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry entry amongst 512 (q4) respectively.
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
    \end{lstlisting}
  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{PageLevelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
    \end{lstlisting} 
\end{itemize}

>>>>

\todo[inline,color=red]{Colin says: Why are we talking about assertions for address translations here? It seems like we should
\todo[inelin]{Colin says: There's no explanation of the split 52+12 \emph{notation} here. If we added such an explanation
(maybe to where physical points-tos are introduced?) and moved this discussion to \ref{sec:overly-restrictive}, this is otherwise
a nice explanation}
discuss physical memory pointsto assertions in general first, then talk about this in \ref{sec:overly-restrictive}}
Given the definition of physical page-pointsto assertion and the root address of virtual-address space as shown in Figure \ref{fig:pagetable}, one can build the physical address-translation for a virtual address (e.g. \textsf{va}) via abstracting the L4-L1 table traversal as the following:
\begin{itemize}
  \item Level-4 Translation (L4): Performs the first level address translation to get the L4 entry (L4E) in Figure \ref{fig:pagetables} by using the masks l4M52 and l4off with \textsf{rtv} virtual base address to get the starting address of the L4 table (L4T), and locate the entry amongst 512 (q1) ones respectively.
    \begin{lstlisting}[language=Coq]
      $\hbox{(\TirNameStyle{{L4translate}})} \quad$ (l4M52 maddr rtv) \$\sim$\ (l4off maddr rtv) $\mapsto_{a}$ {q1} l4e 
    \end{lstlisting}
 \item Level-3 Translation (L3): Performs the second level address translation to get the L3 entry (L3E) in Figure \ref{fig:pagetables} by using the masks l3M52 and l3off with L4 entry (l4e) to get the starting address of the L3 table (L3T), and locate the entry amongst 512 ones (q2) respectively.
    \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L3translate}})}$ (l3M52 maddr l4e) \$\sim$\ (l3off maddr l4e)  $\mapsto_{a}$ {q2} l3e
    \end{lstlisting}
  \item Level-2 Translation (L2): Performs the second level address translation to get the L2 entry (L2E) in Figure \ref{fig:pagetables} by using the masks l2M52 and l2off with L3 entry (l3e) to get the starting address of the L2 table (L2T), and locate the entry amongst 512 ones (q3) respectively.
\begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L2translate}})}$ (l2M52 maddr l3e) \$\sim$\ (l2off maddr l3e)  $\mapsto_{a}$ {q3} l2e
    \end{lstlisting}
  \item Level-1 Translation (L1): Performs the second level address translation to get the L1 entry (L1E) in Figure \ref{fig:pagetables} by using the masks l1M52 and l1off with L2 entry (l2e) to get the starting address of the L1 table (L1T), and locate the entry amongst ones 512 (q4) respectively.
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{L1translate}})}$ (l1M52 maddr l2e) \$\sim$\ (l1off maddr l2e)  $\mapsto_{a}$ {q4} l1e
    \end{lstlisting}
  \item Page Address Level Translation: Final computed physical page-address ($\textsf{addr\_L1}(\vaddr$,$\textsf{l1e}$)) points-to the value stored in the address ($\vpage$).
   \begin{lstlisting}[language=Coq]
    $\hbox{(\TirNameStyle{{PageLevelAccess}})} \qquad$ addr_L1($\vaddr,\textsf{l1e}$) $\mapsto_{p} \vpage$.
    \end{lstlisting} 
\end{itemize}
